
\documentclass[12pt]{report}

\usepackage{CJKutf8}
\usepackage{setspace}
\usepackage{CJK}
%\usepackage{pinyin}

%==
%\usepackage[active]{srcltx}
\usepackage[english]{babel}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage{amsthm}
%\usepackage{fontspec}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{url}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{t1enc}
\usepackage{comment} 
\usepackage{makeidx}
\usepackage{xspace}
\usepackage{subfigure}
%==
\usepackage[a4paper,left=3cm,top=3cm,right=3cm,bottom=3cm,nohead]{geometry}
\setlength{\baselineskip}{10pt}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\input{def}

\doublespacing
\pagestyle{plain}
\begin{document}
\onehalfspacing
%\renewcommand{\baselinestretch}{1} 

\begin{titlepage}
\begin{center}

\begin{CJK}{UTF8}{bkai}
\Large{{國立臺灣大學電機資訊學院電機工程學系\\碩士論文}}\\
\large{{Department of Electrical Engineering}}\\
\large{College of Electrical Engineering and Computer Science}\\
\Large{{National Taiwan University}}\\
\Large{{Master Thesis}}\\

\hspace*{1cm}~\\
\hspace*{1cm}~\\
\hspace*{1cm}~\\
\Large{基於Android NFC卡片模擬進行之人性化認證方案\\
A User-friendly Authentication Solution using NFC Card Emulation on Android }\\
\hspace*{1cm}~\\
\hspace*{1cm}~\\
\hspace*{1cm}~\\

\Large{李鎬\\Lee Haw}\\
\hspace*{1cm}~\\
\hspace*{1cm}~\\

\Large{指導教授：鄭振牟 博士\\Advisor: Chen-Mou Cheng, Ph.D.}\\
\hspace*{1cm}~\\
\hspace*{1cm}~\\


\Large{中華民國 103 年 6 月\\June, 2014}\\

\end{CJK}
\end{center}
\end{titlepage}


\clearpage

\pagenumbering{roman}
\setcounter{page}{1}

\doublespacing
\begin{abstract}

With the services provided on the Internet in our daily life increase dramatically, a secure authentication system becomes more and more important. An insecure authentication system will produce a great threat for users' privacy. In recent years, it is common to see the news of users' credential are stolen by breaking into a website's database. In conclusion, the traditional password-based solution cannot resist to a variety of different attack methods nowadays.

Beside the security issue, the usability is important for an authentication system as well. No matter how secure a system is, users will not adopt an authentication system which is not intuitive.

Therefore, this study implements a simple system, based on digital signature algorithm to authenticate the identity of the user. Take advantages of the increasingly widespread use of mobile devices to enhance the convenience and practicality. Finally, the last part of this thesis shows the comparison between this system and some other existing systems in the viewpoint from security, usability and the deployment ability.


\vspace*{3em}
{\bf Keywords:} \emph{computer security, authentication scheme, digital signature, security and usability, Android host-card-emulation}

\end{abstract}
\input{abstract}

\clearpage

\tableofcontents
\listoffigures
\listoftables
\clearpage

\doublespacing
\pagenumbering{arabic}
\setcounter{page}{1}
\setcounter{tocdepth}{1}

\input{intro}    
\input{preliminaries}
\input{system}
% \input{implement}
\input{discussion}
\input{conclusion}

\printindex

\bibliographystyle{alpha}
\bibliography{nfc_auth_solution}


\end{document}